Figures

### 2019-11-27 manuscript/figures.Rmd
specify map printing

```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/11_map-1.pdf")
```

>>>>

```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/11_map-1.pdf")
```
